---
title: "Setup `swirl` lessons"
author: "Jerid Francom"
date: '`r paste("Updated:", format(Sys.time(), "%b %d, %Y at %r"))`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

The R Markdown document can be used to install and/ or update swirl lessons for this course. The code and process is documented below. 

# Load swirl package

First we will load the `swirl` package.

```{r load-swirl}
library(swirl)
```

# Remove current lessons

Before we download the (current) LIN 380 swirl lessons, let's remove the existing lessons

```{r uninstall-lessons}
uninstall_all_courses(force = TRUE)
```

# Update lessons

Now we can update the lessons with the most current version available. 

```{r install-lessons}
install_course_github(github_username = "lin380", course_name = "swirl")
```

Now you can run the `run_swirl.R` script to get started with the swirl course and select a lesson. Alternatively you can the following commands from the Console: 

```r
library(swirl)
swirl()
```

Then follow the prompts to select the swirl course and select a lesson.
